\normalfont{A statistical analysis on factors that contributed/slowed down the spread of COVID-19}

### 2020-09-07 Manuscript/Manuscript.tex
pub

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[scale=1]{Pic/CorrMatrix_WORLD.pdf}
\caption{The Correlation matrix for the a set of countries accompanied by its heat-map as generated by the following dataset:  }
\label{World_CorrMatrix}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=1]{Pic/Variances-PCA_WORLD.pdf}
\caption{Percentage of variance for each component of the dataset concerning the selected countries. Note that using the first two, the 57.9 $\% $ of variance is captured, as consequence the information lost is 42.1 $\%$}
\label{World_variances}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=1]{Pic/PCA-Loadings_WORLD.pdf}
\caption{2D plot of the loading vector for the dataset of the selected countries normalized on the unitary circle. The features, the date of their collection and unit of measure are the same of Fig. \ref{World_CorrMatrix}}
\label{World_PCA_loadings}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=1]{Pic/World_FULLPCA.pdf}
\caption{The dataset of countries plotted on the two principal components that capture the 57.9 $\% $ of variance. The features, the date of their collection and unit of measure are the same of Fig. \ref{World_CorrMatrix}}
\label{World_FULL_PCA}
\end{center}
\end{figure}
